Polynomial phase estimation by phase unwrapping 1: Identifiability and strong consistency

### 2012-10-31 paper.tex
minor

This paper has considered the estimation of the coefficients of a noisy polynomial phase signal by least squares phase unwrapping (LSU). We have derived conditions under which the polynomial phase estimation problem is identifiable.  Under these conditions, and under some assumptions on the distribution of the noise, the LSU estimator is shown to be strongly consistent. %Simulations are used to show that the LSU has near maximum likelihood performance in the case that the noise is additive white and Gaussian.  
In the second paper in this series~\cite{McKilliam_pps2_2012} we show the LSU estimator to be asymptotically normal and present the results of Monte Carlo simulations that support our asymptotic results.

>>>>

This paper has considered the estimation of the coefficients of a noisy polynomial phase signal by least squares phase unwrapping (LSU). We have derived conditions under which the polynomial phase estimation problem is identifiable.  Under these conditions, and under some assumptions on the distribution of the noise, the LSU estimator is shown to be strongly consistent. %Simulations are used to show that the LSU has near maximum likelihood performance in the case that the noise is additive white and Gaussian.  
In the second paper in this series~\cite{McKilliam_pps2_2012} we show the LSU estimator to be asymptotically normally distributed and present the results of Monte Carlo simulations that support our asymptotic results.
